Nail: A practical interface generator for data formats

### 2015-08-17 paper/thesis/eval.tex
section->chapter

To answer the first question, we used Nail to implement grammars
for seven protocols with a range of challenging features.
Figure~\ref{fig:eval-protocols} summarizes these protocols, the lines
of code for their Nail grammars, and the challenging features that make
the protocols difficult to parse with state-of-the-art parser generators.
We find that despite the challenging aspects of these protocols, Nail is
able to capture the protocols, by relying on its novel features: dependent
fields, streams, and transforms.  In contrast, state-of-the-art parser
generators would be unable to fully handle 5 out of the 7 data formats.
In the rest of this section, we describe the DNS and Zip grammars in
more detail, focusing on how Nail's features enable us to support these
formats.

@@

In Section~\ref{s:design}, we introduced Nail's syntax with a grammar
for DNS packets, shown in Figure~\ref{fig:dns-full}.
The grammar corresponds almost directly to the diagrams in RFC 1035,
which defines DNS~\cite[\S4]{RFC:1035}.  Each DNS packet consists of a
header, a set of question records, and a set of answer records. Domain
names in both queries and answers are encoded as a sequence of labels,
terminated by a zero byte.  Labels are Pascal-style strings, consisting
of a length field followed by that many bytes comprising the label.

>>>>

To answer the first question, we used Nail to implement grammars
for seven protocols with a range of challenging features.
Figure~\ref{fig:eval-protocols} summarizes these protocols, the lines
of code for their Nail grammars, and the challenging features that make
the protocols difficult to parse with state-of-the-art parser generators.
We find that despite the challenging aspects of these protocols, Nail is
able to capture the protocols, by relying on its novel features: dependent
fields, streams, and transforms.  In contrast, state-of-the-art parser
generators would be unable to fully handle 5 out of the 7 data formats.
In the rest of this chapter, we describe the DNS and Zip grammars in
more detail, focusing on how Nail's features enable us to support these
formats.

@@

In Chapter~\ref{s:design}, we introduced Nail's syntax with a grammar
for DNS packets, shown in Figure~\ref{fig:dns-full}.
The grammar corresponds almost directly to the diagrams in RFC 1035,
which defines DNS~\cite[\S4]{RFC:1035}.  Each DNS packet consists of a
header, a set of question records, and a set of answer records. Domain
names in both queries and answers are encoded as a sequence of labels,
terminated by a zero byte.  Labels are Pascal-style strings, consisting
of a length field followed by that many bytes comprising the label.
